Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-08-11 plos/main.tex
Build paper according to plos guidelines.

% Template for PLoS
% Version 3.4 January 2017
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file
% and leave only the final text of your manuscript.
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
% TODO Move copy all the tables in to the file (JEEEEEEZ)
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/lookerup.pdf}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/gambler.pdf}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/ann.pdf}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/fsm.pdf}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
        \includegraphics[width=.5\textwidth]{./assets/FSM16.pdf}
        \caption{\bf Evolved\_FSM\_16: trained to maximise score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{./assets/FSM16noise.pdf}
        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/hmm.pdf}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

A total of \input{./assets/number_of_players.tex}are included, of which
\input{./assets/number_of_stochastic_players.tex}are stochastic.
A standard tournament with 200
turns and a tournament with 5\% noise is
discussed. Due to the inherent stochasticity of these IPD tournaments, these
tournaments were repeated \input{./assets/standard_number_of_repetitions.tex}
times. This allows for a detailed and confident analysis of the performance of
strategies. To illustrate the results considered,
Fig~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
turn of Tit For Tat over all the repetitions. Similarly,
Fig~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
repetition. (We note that it never wins a tournament). Finally
Fig~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
tournament: Tit For Tat does not win any match. (This is due to the fact that it
will either draw with mutual cooperation or defect second).

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_tft_scores.pdf}
        \caption{\bf Scores for Tit for Tat over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_tft_ranks.pdf}
        \caption{\bf Ranks for Tit for Tat over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_tft_wins.pdf}
        \caption{\bf Wins for Tit for Tat over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{table}[!hbtp]
        \centering
        \footnotesize
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$).}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{\bf Standard Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_winners_wins_summary.tex}
        \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{tbl:standard_wins_top_winners}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{tbl:standard_wins}
    \centering
    \footnotesize
        \input{./assets/standard_top_15_wins_summary.tex}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
    \footnotesize
        \input{./assets/standard_top_15_wins_summary.tex}
        \input{./assets/standard_top_15_ranks_summary.tex}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{\bf Standard Tournament: rank in each tournament (ranked by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2 (over 10000
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_HMM\_5 (over 10000)
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16 (over 10000)
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_3}
\end{figure}

@@

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \caption{\bf Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
        (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)
        ~$^{*}$ indicates that the strategy was trained.}
        \footnotesize
        \input{./assets/noisy_top_15_scores_summary.tex}
        \label{tbl:noisy_score}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{./assets/noisy_scores_boxplots.pdf}
        \caption{\bf Noisy (5\%) Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments).}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

>>>>

% Template for PLoS
% Version 3.4 January 2017
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file
% and leave only the final text of your manuscript.
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{lookerup.pdf}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{gambler.pdf}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.9\textwidth]{ann.pdf}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{fsm.pdf}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
        \includegraphics[width=.5\textwidth]{FSM16.pdf}
        \caption{\bf Evolved\_FSM\_16: trained to maximise score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{FSM16noise.pdf}
        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{hmm.pdf}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

A total of 176 are included, of which
53 are stochastic.
A standard tournament with 200
turns and a tournament with 5\% noise is
discussed. Due to the inherent stochasticity of these IPD tournaments, these
tournaments were repeated 50000
times. This allows for a detailed and confident analysis of the performance of
strategies. To illustrate the results considered,
Fig~\ref{fig:tit_for_tat_scores} shows the distribution of the mean score per
turn of Tit For Tat over all the repetitions. Similarly,
Fig~\ref{fig:tit_for_tat_ranks} shows the ranks of of Tit For Tat for each
repetition. (We note that it never wins a tournament). Finally
Fig~\ref{fig:tit_for_tat_wins} shows the number of opponents beaten in any given
tournament: Tit For Tat does not win any match. (This is due to the fact that it
will either draw with mutual cooperation or defect second).

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_scores.pdf}
        \caption{\bf Scores for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_ranks.pdf}
        \caption{\bf Ranks for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_wins.pdf}
        \caption{\bf Wins for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{table}[!hbtp]
        \centering
        \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  2.955 &  0.010 &  2.915 &  2.937 &  2.948 &  2.956 &  2.963 &  2.971 &  2.989 \\
Evolved HMM 5$^{*}$           &  2.954 &  0.014 &  2.903 &  2.931 &  2.945 &  2.954 &  2.964 &  2.977 &  3.007 \\
Evolved FSM 16$^{*}$          &  2.952 &  0.013 &  2.900 &  2.930 &  2.943 &  2.953 &  2.962 &  2.973 &  2.993 \\
PSO Gambler 2\_2\_2$^{*}$       &  2.938 &  0.013 &  2.884 &  2.914 &  2.930 &  2.940 &  2.948 &  2.957 &  2.972 \\
Evolved FSM 16 Noise 05$^{*}$ &  2.919 &  0.013 &  2.874 &  2.898 &  2.910 &  2.919 &  2.928 &  2.939 &  2.965 \\
PSO Gambler 1\_1\_1$^{*}$       &  2.912 &  0.023 &  2.805 &  2.874 &  2.896 &  2.912 &  2.928 &  2.950 &  3.012 \\
Evolved ANN 5$^{*}$           &  2.912 &  0.010 &  2.871 &  2.894 &  2.905 &  2.912 &  2.919 &  2.928 &  2.945 \\
Evolved FSM 4$^{*}$           &  2.910 &  0.012 &  2.867 &  2.889 &  2.901 &  2.910 &  2.918 &  2.929 &  2.943 \\
Evolved ANN$^{*}$             &  2.907 &  0.010 &  2.865 &  2.890 &  2.900 &  2.908 &  2.914 &  2.923 &  2.942 \\
PSO Gambler Mem1$^{*}$        &  2.901 &  0.025 &  2.783 &  2.858 &  2.884 &  2.901 &  2.919 &  2.942 &  2.994 \\
Evolved ANN 5 Noise 05$^{*}$  &  2.864 &  0.008 &  2.830 &  2.850 &  2.858 &  2.865 &  2.870 &  2.877 &  2.891 \\
DBS                           &  2.857 &  0.009 &  2.823 &  2.842 &  2.851 &  2.857 &  2.863 &  2.872 &  2.899 \\
Winner12                      &  2.849 &  0.008 &  2.820 &  2.836 &  2.844 &  2.850 &  2.855 &  2.862 &  2.874 \\
Fool Me Once                  &  2.844 &  0.008 &  2.818 &  2.830 &  2.838 &  2.844 &  2.850 &  2.857 &  2.882 \\
Omega TFT: 3, 8               &  2.841 &  0.011 &  2.800 &  2.822 &  2.833 &  2.841 &  2.849 &  2.859 &  2.882 \\
\bottomrule
\end{tabular}
        \caption{\bf Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over 50000 tournaments).
        The leaderboard is dominated by the trained strategies (indicated by a
        $^{*}$).}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{standard_scores_boxplots.pdf}
        \caption{\bf Standard Tournament: Mean score per turn (ranked by median
        over
        50000 tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{standard_scores_heatmap.pdf}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over 50000 tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        50000 tournaments).}
        \label{tbl:standard_wins_top_winners}
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &     mean &    std &  min &     5\% &    25\% &    50\% &    75\% &    95\% &  max \\
\midrule
Aggravater          &  161.595 &  0.862 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
Defector            &  161.605 &  0.864 &  160 &  160.0 &  161.0 &  162.0 &  162.0 &  163.0 &  163 \\
CS                  &  159.646 &  1.005 &  155 &  158.0 &  159.0 &  160.0 &  160.0 &  161.0 &  161 \\
ZD-Extort-4         &  150.598 &  2.662 &  138 &  146.0 &  149.0 &  151.0 &  152.0 &  155.0 &  162 \\
Handshake           &  149.552 &  1.754 &  142 &  147.0 &  148.0 &  150.0 &  151.0 &  152.0 &  154 \\
ZD-Extort-2         &  146.094 &  3.445 &  129 &  140.0 &  144.0 &  146.0 &  148.0 &  152.0 &  160 \\
ZD-Extort-2 v2      &  146.291 &  3.425 &  131 &  141.0 &  144.0 &  146.0 &  149.0 &  152.0 &  160 \\
Winner21            &  139.946 &  1.225 &  136 &  138.0 &  139.0 &  140.0 &  141.0 &  142.0 &  143 \\
TF2                 &  138.240 &  1.700 &  130 &  135.0 &  137.0 &  138.0 &  139.0 &  141.0 &  143 \\
TF1                 &  135.692 &  1.408 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  138.0 &  140 \\
Naive Prober: 0.1   &  136.016 &  2.504 &  127 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  147 \\
Feld: 1.0, 0.5, 200 &  136.087 &  1.696 &  130 &  133.0 &  135.0 &  136.0 &  137.0 &  139.0 &  144 \\
Joss: 0.9           &  136.015 &  2.503 &  126 &  132.0 &  134.0 &  136.0 &  138.0 &  140.0 &  146 \\
Predator            &  133.718 &  1.385 &  129 &  131.0 &  133.0 &  134.0 &  135.0 &  136.0 &  138 \\
SolutionB5          &  125.843 &  1.509 &  120 &  123.0 &  125.0 &  126.0 &  127.0 &  128.0 &  131 \\
\bottomrule
\end{tabular}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{standard_wins_boxplots.pdf}
        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \caption{\bf Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        50000 tournaments).}
        \label{tbl:standard_wins}
    \centering
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &  48.259 &  1.336 &   43 &  46.0 &  47.0 &  48.0 &  49.0 &  50.0 &   53 \\
Evolved HMM 5$^{*}$           &  41.358 &  1.221 &   36 &  39.0 &  41.0 &  41.0 &  42.0 &  43.0 &   45 \\
Evolved FSM 16$^{*}$          &  56.978 &  1.099 &   51 &  55.0 &  56.0 &  57.0 &  58.0 &  59.0 &   60 \\
PSO Gambler 2\_2\_2$^{*}$       &  40.692 &  1.089 &   36 &  39.0 &  40.0 &  41.0 &  41.0 &  42.0 &   45 \\
Evolved FSM 16 Noise 05$^{*}$ &  40.070 &  1.673 &   34 &  37.0 &  39.0 &  40.0 &  41.0 &  43.0 &   47 \\
PSO Gambler 1\_1\_1$^{*}$       &  45.005 &  1.595 &   38 &  42.0 &  44.0 &  45.0 &  46.0 &  48.0 &   51 \\
Evolved ANN 5$^{*}$           &  43.224 &  0.674 &   41 &  42.0 &  43.0 &  43.0 &  44.0 &  44.0 &   47 \\
Evolved FSM 4$^{*}$           &  37.227 &  0.951 &   34 &  36.0 &  37.0 &  37.0 &  38.0 &  39.0 &   41 \\
Evolved ANN$^{*}$             &  43.100 &  1.021 &   40 &  42.0 &  42.0 &  43.0 &  44.0 &  45.0 &   48 \\
PSO Gambler Mem1$^{*}$        &  43.444 &  1.837 &   34 &  40.0 &  42.0 &  43.0 &  45.0 &  46.0 &   51 \\
Evolved ANN 5 Noise 05$^{*}$  &  33.711 &  1.125 &   30 &  32.0 &  33.0 &  34.0 &  34.0 &  35.0 &   38 \\
DBS                           &  32.329 &  1.198 &   28 &  30.0 &  32.0 &  32.0 &  33.0 &  34.0 &   38 \\
Winner12                      &  40.179 &  1.037 &   36 &  39.0 &  39.0 &  40.0 &  41.0 &  42.0 &   44 \\
Fool Me Once                  &  50.121 &  0.422 &   48 &  50.0 &  50.0 &  50.0 &  50.0 &  51.0 &   52 \\
Omega TFT: 3, 8               &  35.157 &  0.859 &   32 &  34.0 &  35.0 &  35.0 &  36.0 &  37.0 &   39 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \caption{\bf Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        50000 tournaments).}
    \footnotesize
\begin{tabular}{lrrrrrrrrr}
\toprule
{} &    mean &    std &  min &    5\% &   25\% &   50\% &   75\% &   95\% &  max \\
\midrule
EvolvedLookerUp2\_2\_2$^{*}$    &   2.173 &  1.070 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   4.0 &    8 \\
Evolved HMM 5$^{*}$           &   2.321 &  1.275 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
Evolved FSM 16$^{*}$          &   2.489 &  1.299 &    1 &   1.0 &   1.0 &   2.0 &   3.0 &   5.0 &   10 \\
PSO Gambler 2\_2\_2$^{*}$       &   3.961 &  1.525 &    1 &   2.0 &   3.0 &   4.0 &   5.0 &   7.0 &   10 \\
Evolved FSM 16 Noise 05$^{*}$ &   6.300 &  1.688 &    1 &   4.0 &   5.0 &   6.0 &   7.0 &   9.0 &   11 \\
PSO Gambler 1\_1\_1$^{*}$       &   7.082 &  2.499 &    1 &   3.0 &   5.0 &   7.0 &   9.0 &  10.0 &   17 \\
Evolved ANN 5$^{*}$           &   7.287 &  1.523 &    2 &   5.0 &   6.0 &   7.0 &   8.0 &  10.0 &   11 \\
Evolved FSM 4$^{*}$           &   7.527 &  1.631 &    2 &   5.0 &   6.0 &   8.0 &   9.0 &  10.0 &   12 \\
Evolved ANN$^{*}$             &   7.901 &  1.450 &    2 &   5.0 &   7.0 &   8.0 &   9.0 &  10.0 &   12 \\
PSO Gambler Mem1$^{*}$        &   8.222 &  2.535 &    1 &   4.0 &   6.0 &   9.0 &  10.0 &  12.0 &   20 \\
Evolved ANN 5 Noise 05$^{*}$  &  11.362 &  0.872 &    8 &  10.0 &  11.0 &  11.0 &  12.0 &  13.0 &   16 \\
DBS                           &  12.197 &  1.125 &    9 &  11.0 &  11.0 &  12.0 &  13.0 &  14.0 &   16 \\
Winner12                      &  13.221 &  1.137 &    9 &  11.0 &  12.0 &  13.0 &  14.0 &  15.0 &   17 \\
Fool Me Once                  &  13.960 &  1.083 &    9 &  12.0 &  13.0 &  14.0 &  15.0 &  15.0 &   17 \\
Omega TFT: 3, 8               &  14.275 &  1.301 &    9 &  12.0 &  13.0 &  15.0 &  15.0 &  16.0 &   19 \\
\bottomrule
\end{tabular}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.8\paperwidth]{standard_ranks_boxplots.pdf}
        \caption{\bf Standard Tournament: rank in each tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2 (over 10000
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_HMM\_5 (over 10000)
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16 (over 10000)
        repetitions)}
        \label{fig:comparison_cooperation_heatmaps_standard_3}
\end{figure}

@@

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \caption{\bf Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
        (ranked by median over 50000 tournaments)
        ~$^{*}$ indicates that the strategy was trained.}
        \footnotesize
        \begin{tabular}{lrrrrrrrrr}
        \toprule
        {} &   mean &    std &    min &     5\% &    25\% &    50\% &    75\% &    95\% &    max \\
        \midrule
        DBS                              &  2.573 &  0.025 &  2.474 &  2.533 &  2.556 &  2.573 &  2.589 &  2.614 &  2.675 \\
        Evolved ANN 5 Noise 05$^{*}$     &  2.534 &  0.025 &  2.418 &  2.492 &  2.517 &  2.534 &  2.551 &  2.575 &  2.629 \\
        Evolved FSM 16 Noise 05$^{*}$    &  2.515 &  0.031 &  2.374 &  2.464 &  2.494 &  2.515 &  2.536 &  2.565 &  2.642 \\
        Evolved ANN 5$^{*}$              &  2.410 &  0.030 &  2.273 &  2.359 &  2.389 &  2.410 &  2.430 &  2.459 &  2.536 \\
        Evolved FSM 4$^{*}$              &  2.393 &  0.027 &  2.286 &  2.348 &  2.374 &  2.393 &  2.411 &  2.437 &  2.505 \\
        Evolved HMM 5$^{*}$              &  2.392 &  0.026 &  2.289 &  2.348 &  2.374 &  2.392 &  2.409 &  2.435 &  2.493 \\
        Level Punisher                   &  2.388 &  0.025 &  2.281 &  2.347 &  2.372 &  2.389 &  2.405 &  2.429 &  2.503 \\
        Omega TFT: 3, 8                  &  2.387 &  0.026 &  2.270 &  2.344 &  2.370 &  2.388 &  2.405 &  2.430 &  2.498 \\
        Spiteful Tit For Tat             &  2.383 &  0.030 &  2.259 &  2.334 &  2.363 &  2.383 &  2.403 &  2.432 &  2.517 \\
        Evolved FSM 16$^{*}$             &  2.375 &  0.029 &  2.239 &  2.326 &  2.355 &  2.375 &  2.395 &  2.423 &  2.507 \\
        PSO Gambler 2\_2\_2 Noise 05$^{*}$ &  2.371 &  0.029 &  2.250 &  2.323 &  2.352 &  2.371 &  2.390 &  2.418 &  2.480 \\
        Adaptive                         &  2.369 &  0.038 &  2.217 &  2.306 &  2.344 &  2.369 &  2.395 &  2.431 &  2.524 \\
        Evolved ANN$^{*}$                &  2.365 &  0.022 &  2.270 &  2.329 &  2.351 &  2.366 &  2.380 &  2.401 &  2.483 \\
        Math Constant Hunter             &  2.344 &  0.022 &  2.257 &  2.308 &  2.329 &  2.344 &  2.359 &  2.382 &  2.445 \\
        Gradual                          &  2.341 &  0.021 &  2.248 &  2.306 &  2.327 &  2.341 &  2.355 &  2.376 &  2.429 \\
        \bottomrule
        \end{tabular}
        \label{tbl:noisy_score}
\end{table}
